### 2012-05-02 inst/examples/policycosts/stochastic_norms.Rmd
updated with profits

# Asymmetric Policy Costs 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim}
c2 <- 4
penalty <- free_decrease(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

@@

### Plots

@@

Profits

``` {r rep1profit, cache=cache}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit_fishing)) +
  geom_line(aes(time, policy_cost), col="darkblue") 
````

>>>>

# Policy Costs 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim}
c2 <- 4
penalty <- fixed(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

@@

# Plots

@@

## Profits

``` {r rep1profit, cache=cache}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit_fishing)) +
  geom_line(aes(time, policy_cost), col="darkblue")

````

``` {r policycost, cache=cache}
costs <- dt[ , sum(policy_cost), by=reps]
profits <-dt[ , sum(profit_fishing), by=reps]

qplot(costs$V1)
qplot(profits$V1)
qplot(profits-costs$V1)
````
